%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Side Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Optimize Explorations for Uncharted Destinations} % Organisation
    {Vacation Planner} % Project
    {} % Location
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Led the technical engineering design, architecture design, and database implementation.}
        \item {Developed an efficient backend architecture to optimize travel itineraries and activities for users exploring unfamiliar destinations.}
        \item {\textbf{Tech Stack:} NodeJS, Fastify, AWS (\textit{EC2, Lambda}), Mercurius, GraphQL, Angular}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {National Voluntary Association} % Organisation
    {LMS Platform Integration} % Project
    {} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Spearheaded the design of a microservices application to integrate an LMS (Learning Management System) with proprietary services.}
        \item {Architected the overall system, defined the microservices architecture, established communication patterns, and designed the DB structure.}
        \item {\textbf{Tech Stack:} Java, Quarkus, AWS (\textit{EC2, Lambda, API Gateway, ECR, SQS, Amplify}), Svelte}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Final Project for High School graduation} % Organisation
    {Optical Wheelchair} % Project
    {} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a proof-of-concept electric wheelchair operated by facial expressions and movements.}
        \item {Aimed to enhance the autonomy of tetraplegic individuals through facial recognition technology.}
        \item {Received national awards (e.g. 
            \href{https://www.maketocare.it/?sc_lang=en}{'MakeToCare'},
            \href{https://fast.mi.it/i-giovani-e-le-scienze/}{'I giovani e le scienze'}
            ) and participated in international fairs.}
        \item {Featured on RAI 2, one of the main channels of state-owned TV.}
        \item {Presented project in Silicon Valley, engaging with startup incubators and entrepreneurs as a result of competition wins.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
